Analysis of competitive surfing tournaments with generalized Bradley-Terry

### 2021-08-25 inst/surfing.Rmd
use PDF not PNG in surfing_jsa [and create them in surfing.Rmd]

```{r showsurfingmaxppie, echo=FALSE, fig.height=8,fig.cap="dot chart of result"}
dotchart(surfing_maxp)
dotchart(log10(surfing_maxp))
pie(surfing_maxp)
jj <- log(surfing_maxp)
kk <- log(surfing_pairs_maxp)
names(jj) <- NULL
names(kk) <- NULL
l <- c(-4.6, -1.5)
dotchart(log(surfing_maxp),pch=NA,xlim=l)
mydotchart(jj,col="red" ,pch=16,xlim=l,xaxt='n',frame.plot=FALSE)
mydotchart(kk,col="blue",pch=16,xlim=l,xaxt='n',frame.plot=FALSE)
```

@@

```{r directlogplotofstrengths,cache=TRUE}
jjO <- surfing_table$points[wanted]
names(jjO) <- rownames(surfing_table)[wanted]
jjL <- surfing_maxp
jjO <- ordertrans(jjO)
jjL <- ordertrans(jjL)
plot(jjO,jjL,pch=16,log='xy',xlab='points',ylab='maximum likelihood strength')
fit <- lm(log10(jjL)~log10(jjO))
summary(fit)
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)
```

@@

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
rL <- sort(surfing_maxp,decreasing=TRUE)
rL[] <- seq_along(rL)    # likelihood-based rank
rO <- seq_len(nrow(surfing_table[wanted,]))
names(rO) <- rownames(surfing_table)[wanted]
rO
rL
sort(names(rO))
sort(names(rO))
sort(names(rO))==sort(names(rO))
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
```

@@

```{r plotwidep}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype wide",ylab="support")
abline(h= -2,lty=2)
```

>>>>

```{r showsurfingmaxppie, echo=FALSE, fig.height=8,fig.cap="dot chart of result"}
dotchart(surfing_maxp)
dotchart(log10(surfing_maxp))
pie(surfing_maxp)
pdf(file="showsurfingmaxppie.pdf")
pie(surfing_maxp)
dev.off()
jj <- log(surfing_maxp)
kk <- log(surfing_pairs_maxp)
names(jj) <- NULL
names(kk) <- NULL
l <- c(-4.6, -1.5)
dotchart(log(surfing_maxp),pch=NA,xlim=l)
mydotchart(jj,col="red" ,pch=16,xlim=l,xaxt='n',frame.plot=FALSE)
mydotchart(kk,col="blue",pch=16,xlim=l,xaxt='n',frame.plot=FALSE)
```

@@

```{r directlogplotofstrengths,cache=TRUE}
jjO <- surfing_table$points[wanted]
names(jjO) <- rownames(surfing_table)[wanted]
jjL <- surfing_maxp
jjO <- ordertrans(jjO)
jjL <- ordertrans(jjL)
plot(jjO,jjL,pch=16,log='xy',xlab='points',ylab='maximum likelihood strength')
fit <- lm(log10(jjL)~log10(jjO))
summary(fit)
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)

pdf(file="directlogplotofstrengths.pdf")
plot(jjO,jjL,pch=16,log='xy',xlab='points',ylab='maximum likelihood strength')
fit <- lm(log10(jjL)~log10(jjO))
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)
dev.off()
```

@@

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
rL <- sort(surfing_maxp,decreasing=TRUE)
rL[] <- seq_along(rL)    # likelihood-based rank
rO <- seq_len(nrow(surfing_table[wanted,]))
names(rO) <- rownames(surfing_table)[wanted]
rO
rL
sort(names(rO))
sort(names(rO))
sort(names(rO))==sort(names(rO))
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
pdf(file="ordertransplotplot.pdf")
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
dev.off()
```

@@

```{r plotwidep}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype wide",ylab="support")
abline(h= -2,lty=2)
pdf(file="plotwidep.pdf")
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype wide",ylab="support")
abline(h= -2,lty=2)
dev.off()
```

### 2021-08-25 inst/surfing_jsa.tex
use PDF not PNG in surfing_jsa [and create them in surfing.Rmd]

\begin{figure}[h]
\includegraphics[width=4in]{surfing_files/figure-html/showsurfingmaxppie-3.png} % Pie chart of strengths
\caption{Pie chart\label{piechartmax} showing maximum likelihood strengths of the 23 competitors.  Note the
dominance of Ferreira, Florence, and Medina}
\end{figure}

\begin{figure}[h]
\includegraphics[width=4in]{surfing_files/figure-html/directlogplotofstrengths-1.png}
\caption{Scatterplot of points scored  \label{compare_likelihood_points} 
against maximum likelihood estimates}
\end{figure}

\begin{figure}[h]
\includegraphics[width=4in]{surfing_files/figure-html/ordertransplotplot-1.png}
\caption{Scatterplot of ranks \label{compare_likelihood_points_rankings} of points-based ranking
against likelihood-based ranking.  Note the anomalous position of
Florence}
\end{figure}

\begin{figure}[h]
  \includegraphics[width=4in]{surfing_files/figure-html/plotwidep-1.png}
\caption{Profile support \label{brazilian_wavetype_support} for the
  Brazilian wavetype reified entity.  The horizontal axis specifies a
  particular strength for Brazilian wavetype, and the height of the
  curve gives the support conditional on the x-axis}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=4in]{showsurfingmaxppie.pdf} % Pie chart of strengths
\caption{Pie chart\label{piechartmax} showing maximum likelihood strengths of the 23 competitors.  Note the
dominance of Ferreira, Florence, and Medina}
\end{figure}

\begin{figure}[h]
\includegraphics[width=4in]{directlogplotofstrengths.pdf}
\caption{Scatterplot of points scored  \label{compare_likelihood_points} 
against maximum likelihood estimates}
\end{figure}

\begin{figure}[h]
\includegraphics[width=4in]{ordertransplotplot.pdf}
\caption{Scatterplot of ranks \label{compare_likelihood_points_rankings} of points-based ranking
against likelihood-based ranking.  Note the anomalous position of
Florence}
\end{figure}

\begin{figure}[h]
  \includegraphics[width=4in]{plotwidep.pdf}
\caption{Profile support \label{brazilian_wavetype_support} for the
  Brazilian wavetype reified entity.  The horizontal axis specifies a
  particular strength for Brazilian wavetype, and the height of the
  curve gives the support conditional on the x-axis}
\end{figure}
